### 2018-12-21 tex/paper.tex
Overview modified.

\mysection{Accurate Submodular Extensions from LP Relaxations}

Different choices of extensions $F$ change the domain in problem \eqref{eq:min_upper_bound}, leading to different upper bounds on the log-partition function. How does one come up with an extension which yields the tightest bound?

@@

  Motivated by this connection, we ask if one can introduce a temperature parameter to our problem \eqref{eq:min_upper_bound} and transform it to an LP relaxation in the limit $T \to 0$? We can then hope to use accurate LP relaxations of MAP problems known in literature to find good submodular extensionsfor different classes of energy functions.

We answer this question in affirmative. Specifically, in the following two sections we show how one can select the set encoding and submodular extension to convert problem \eqref{eq:min_upper_bound} to accurate LP relaxations for Potts, hierarchical Potts and higher-order Potts models. In fact, when the LP relaxation has tightness guarantees, we obtain worst-case optimal submodular extensions - a notion we elucidate shortly.

>>>>

\mysection{Overview: Accurate Submodular Extensions from LP Relaxations}

Different choices of extensions $F$ change the domain in problem \eqref{eq:min_upper_bound}, leading to different upper bounds on the log-partition function. How does one come up with accurate extensions for different classes of CRF energy functions? Is it possible to identify optimal extensions which yields the tightest bound?

@@

  Motivated by this connection, we ask if one can introduce a temperature parameter to our problem \eqref{eq:min_upper_bound} and transform it to an LP relaxation in the limit $T \to 0$? We can then hope to use accurate LP relaxations of MAP problems known in literature to find good submodular extensions for different classes of energy functions.

We answer this question in affirmative. Specifically, in the following two sections we show how one can select the set encoding and submodular extension to convert problem \eqref{eq:min_upper_bound} to accurate LP relaxations for Potts, hierarchical Potts and higher-order diversity models. In fact, when the LP relaxation has tightness guarantees, we obtain worst-case optimal submodular extensions - a notion we elucidate shortly.
